RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-04-27 manuscripts/manuscript.Rmd
final revisions

If the location parameter with which the `nexml_read()` method is
invoked is recognized as a URL, the method will automatically download
the document to the local working directory and read it from there. This
gives convenient and rapid access to phylogenetic data published in
NeXML format on the web, such as the content of the phylogenetic data
repository TreeBASE [@Piel_2002; @Piel_2009]. For example, the following plots a
tree in TreeBASE (using ape's plot function):

@@

The `RNeXML` interface described above for built-in metadata allows
users to create precise and semantically rich annotations without 
confronting any of the complexity of namespaces and ontologies.
Nevertheless, advanced users may desire the explicit control over
these semantic tools that takes full advantage of the flexibility
and extensibility of the NeXML specification [@Vos2012; @Parr2011].
In this section we detail how to accomplish these more complex uses
in RNeXML.

@@

The goals for continued development of `RNeXML` revolve primarily
around better interoperability with other existing phylogenetic data
representations in R, such those found in the `phylobase` package
[@phylobase]; and better integration of the rich metadata semantics
found in ontologies defined in the Web Ontology Language (OWL),
including programmatic access to machine reasoning with such metadata.

>>>>

If the location parameter with which the `nexml_read()` method is
invoked is recognized as a URL, the method will automatically download
the document to the local working directory and read it from there. This
gives convenient and rapid access to phylogenetic data published in
NeXML format on the web, such as the content of the phylogenetic data
repository TreeBASE [@Piel_2002]. For example, the following plots a
tree in TreeBASE (using ape's plot function):

@@

The `RNeXML` interface described above for built-in metadata allows
users to create precise and semantically rich annotations without 
confronting any of the complexity of namespaces and ontologies.
Nevertheless, advanced users may desire the explicit control over
these semantic tools that takes full advantage of the flexibility
and extensibility of the NeXML specification [@Vos_2012; @Parr2011].
In this section we detail how to accomplish these more complex uses
in RNeXML.

@@

The goals for continued development of `RNeXML` revolve primarily
around better interoperability with other existing phylogenetic data
representations in R, such as those found in the `phylobase` package
[@phylobase]; and better integration of the rich metadata semantics
found in ontologies defined in the Web Ontology Language (OWL),
including programmatic access to machine reasoning with such metadata.
